### 2022-12-14 README.Rmd
update readme

## ppmData is an R package that can be used to set up a quadrature scheme for spatial point processes modelling and could be used in [ecomix](https://github.com/skiptoniam/ecomix) to run multiple species Point Processes.

@@

```{r, message=FALSE}
library(ppmData)
path <- system.file("extdata", package = "ppmData")
lst <- list.files(path=path, pattern='*.tif',full.names = TRUE)
preds <- rast(lst)
presences <- subset(snails,SpeciesID %in% "Tasmaphena sinclairi")
npoints <- 1000
ppmdata1 <- ppmData(npoints = npoints, presences=presences,
                    window = preds[[1]], covariates=preds)
```

@@

>>>>

## ppmData is an R package that can be used to set up a quadrature scheme for spatial point processes modelling and could be used in other packages, like [ecomix](https://github.com/skiptoniam/ecomix) to run marked poisson point processes.

@@

```{r, message=FALSE}
library(ppmData)
path <- system.file("extdata", package = "ppmData")
lst <- list.files(path=path, pattern='*.tif',full.names = TRUE)
covariates <- rast(lst)
presences <- subset(snails,SpeciesID %in% "Tasmaphena sinclairi")
npoints <- 1000
ppmdata1 <- ppmData(npoints = npoints, presences=presences,
                    window = covariates[[1]], covariates=covariates)
```

@@

Here is a brief example of how you might fit a ppm using `glm`.

```{r, warning=FALSE}
ppp <- ppmdata1$ppmData
form  <- presence/weights ~ poly(annual_mean_precip, degree = 2) + 
                            poly(annual_mean_temp, degree = 2) + 
                            poly(distance_from_main_roads, degree = 2)

ft.ppm <- glm(formula = form, data = ppp,
              weights = as.numeric(ppp$weights),
              family = poisson())
```

One we have fitted the model, we might want to predict the relative intensity
across the window, this will give us something similar to the expected count of 
species presences per-cell.

```{r,fig.width=6, fig.height=6, fig.cap=""}
pred <- predict(covariates,
                ft.ppm,
                type="response")
plot(pred*prod(res(pred))) # scale response by area of cell.
```
